% --------------------------------------------------------------
% This is all preamble stuff that you don't have to worry about.
% Head down to where it says "Start here"
% --------------------------------------------------------------
 
\documentclass[12pt]{article}
 
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
 
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
 
\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\newenvironment{solution}{\begin{proof}[Solution]}{\end{proof}}
 
\begin{document}
 
\title{Project 1: Paper Towels}
\date{}

\maketitle

Why do we pay more money for certain brands of products when cheaper ones exist? Are they really better? Some people may tell you yes and others may tell you no. However, it is likely this is based on personal experience and not actual quantifiable testing.

The purpose of this project is to introduce you to some common questions and techniques that arise when collecting and analyzing data. The data that will be collected in this project will be used throughout this course. \\

\noindent
\textbf{Requirements:}

\begin{itemize}
	\item Sewing hoop
	\item 10 Paper towels
	\item Eye dropper
	\item Fishing weights
	\item Paper for recording results
\end{itemize}

\noindent
Form a team of 3 people. Each person will perform a specific task:

\begin{itemize}
	\item{Paper towel (PT) manager}
	\item{Water and weight (WW) placer}
	\item{Data recorder}
\end{itemize}

For each towel, the PT manager should place it in the sewing hoop and hold it. Next, the placer should place three drops of water in a triangle pattern in the center of the towel. Once the water has been absorbed, the placer should start adding weights to the towel one at a time until the towel tears. Finally, the data recorder should be observing the process and recording data and information on each experiment. Data should consist of how many weights the towel supported before tearing. Information should consist of anything "interesting" or "weird" that happened during each experiment.

Once you have completed all ten experiments, put the names of your group members on your data sheets and turn them in to the teacher.
 
\end{document}