% Template from https://www.overleaf.com/latex/templates/chapter-review-notes/npqqbrvfkwqh
\documentclass[11pt]{article}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}	
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{multirow,booktabs}
\usepackage[table]{xcolor}
\usepackage{fullpage}
\usepackage{lastpage}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{wrapfig}
\usepackage{setspace}
\usepackage{calc}
\usepackage{multicol}
\usepackage{cancel}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage[margin=3cm]{geometry}
\usepackage{amsmath}
\newlength{\tabcont}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}
\usepackage{empheq}
\usepackage{framed}
\usepackage[most]{tcolorbox}
\usepackage{xcolor}
\colorlet{shadecolor}{orange!15}
\parindent 0in
\parskip 12pt
\geometry{margin=1in, headsep=0.25in}
\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{reg}{Rule}
\newtheorem{exer}{Exercise}
\newtheorem{note}{Note}
\begin{document}
\title{Title}

\thispagestyle{empty}

\begin{center}
{\LARGE \bf Test 2} \\
{\large Probability \& Statistics} \\
{\large Show all work. Write all answers on exam. Use back of page when necessary. } \\
\end{center}
\section*{Question 1 (20 pts.)}

Let $Y$ be a random variable with distribution $p(y)$ given in the following table:

\begin{table}[h]
	\centering
	\begin{tabular}{lr}
		\hline
		y & $p(y)$ \\
		\hline
		1 & 0.4 \\
		2 & 0.3 \\
		3 & 0.2 \\
		4 & 0.1 \\
		\hline
	\end{tabular}
\end{table}

\noindent Calculate $E[Y]$, $E[5Y+2]$, $E\left[ Y^2 \right]$, and $V[Y]$. Use any valid method to calculate $V[Y]$.

\newpage

\section*{Question 2 (20 pts.)}

You are given

$$
	\begin{aligned}
		E[Y] & = 11 \\
		E[Y^2] & = 169 \\
		E[Y^3] & = 2500
	\end{aligned}
$$

\noindent Calculate the following:

\begin{enumerate}
	\item $E[2Y - 3Y^2 + 5Y^3]$
	\item $V[Y]$
\end{enumerate}

\newpage

\section*{Question 3 (20 pts.)}

A potential customer for an \$85,000 fire insurance policy possesses a home in an area that, according to experience, may sustain a total (100\%) loss in a given year with probability 0.005 and a 50\% loss with probability 0.05. Assuming these are the only losses the policy can sustain, show that the premium that must be charged on all \$85,000 policies in this area is \$2,550.

\newpage

\section*{Question 4 (20 pts.)}

Show that the binomial distribution satisfies the second law of probability, i.e. show that the sum of all probabilities of the binomial distribution sums to 1.

\newpage

\section*{Question 5 (20 pts.)}

A fire-detection device utilizes three temperature-sensitive cells acting independently of each other in such a manner that any one or more may activate the alarm. Each cell has a probability of 0.8 of activating the alarm when the temperature reaches $100^\circ$ Celsius or more. Let $Y$ equal the number of cells activating the alarm when the temperature reaches $100^\circ$ Celsius.

\begin{enumerate}
	\item What type of experiment is this? Why?
	\item What is the probability that the alarm will function when the temperature reaches $100^\circ$ Celsius?
	\item Calculate $E[Y]$ and $V[Y]$.
\end{enumerate}

\newpage

\section*{Question 6 (20 pts.)}

A certified public accountant (CPA) has found that 4 of 10 company audits contain substantial errors. If the CPA audits a series of company accounts, let $Y$ equal the audit number of the first company that has substantial errors.

\begin{enumerate}
	\item What type of experiment is this? Why?
	\item What is a success? What is the probability of success?
	\item What is the probability that the first company account containing substantial errors is the third one to be audited?
	\item What is the probability that the first company account to contain substantial errors will occur on or after the third audited account?
\end{enumerate}

\end{document}
