% Template from https://www.overleaf.com/latex/templates/chapter-review-notes/npqqbrvfkwqh
\documentclass[11pt]{article}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}	
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{multirow,booktabs}
\usepackage[table]{xcolor}
\usepackage{fullpage}
\usepackage{lastpage}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{wrapfig}
\usepackage{setspace}
\usepackage{calc}
\usepackage{multicol}
\usepackage{cancel}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage[margin=3cm]{geometry}
\usepackage{amsmath}
\newlength{\tabcont}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}
\usepackage{empheq}
\usepackage{framed}
\usepackage[most]{tcolorbox}
\usepackage{xcolor}
\colorlet{shadecolor}{orange!15}
\parindent 0in
\parskip 12pt
\geometry{margin=1in, headsep=0.25in}
\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{reg}{Rule}
\newtheorem{exer}{Exercise}
\newtheorem{note}{Note}
\begin{document}
\title{Title}

\thispagestyle{empty}

\begin{center}
{\LARGE \bf Test 1} \\
{\large Probability \& Statistics} \\
{\large Show all work. Write all answers on exam. Use back of page when necessary. } \\
\end{center}
\section*{Question 1 (25 pts.)}

An experiment results in the following 5 observations: 10.0, 11.5, 10.8,  8.4,  9.8

\begin{enumerate}
	\item Calculate the sample mean, $\bar{y}$.
	\item Calculate the sample variance, $s^2$.
	\item Calculate the sample standard deviation, $s$.
	\item Assuming the data are bell-shaped, determine an interval containing approximately 95\% of the data.
\end{enumerate}

\section*{Solution}

\begin{enumerate}
	\item
		$$
			\bar{y} = \frac{10.0 + 11.5 + 10.8 +  8.4 +  9.8}{5} = 10.1
		$$
	\item
		$$
			s^2 = \frac{(10.0-10.1)^2 + (11.5-10.1)^2  + (10.8-10.1)^2  + (8.4-10.1)^2  + (9.8-10.1)^2 }{4} = 1.36
		$$
	\item
		$$
			s = \sqrt{s^2} = \sqrt{1.36} = 1.16619
		$$
	\item
		$$
			\begin{aligned}
				\left( \bar{y} - 2s, \bar{y} + 2s \right) \\
				\left( 7.76762, 12.43238 \right)
			\end{aligned}
		$$
\end{enumerate}

\newpage

\section*{Question 2 (25 pts.)}

If we wish to expand $(x + y)^5$, what is the coefficient of $x^3y^2$?

\section*{Solution}

Using the binomial expansion, we know that the coefficient will be ${5 \choose 2}$.

$$
	{5 \choose 2} = \frac{5!}{2!3!} = \frac{5\cdot4}{2\cdot1} = 10
$$

\newpage

\section*{Question 3 (25 pts.)}

A business office orders paper supplies from one of three vendors: $V_1$, $V_2$, or $V_3$. Orders are to be placed on two successive days, one order per day. Thus, $(V_2, V_3)$ might denote that vendor $V_2$ gets the order on the first day and vendor $V_3$ gets the order on the second day.

\begin{enumerate}
	\item List the sample points in this experiment of ordering paper on two successive days.
	\item Assume the vendors are selected at random each day and assign a probability to each sample point.
	\item Let $A$ denote the event that the same vendor gets both orders and $B$ the event that $V_2$ gets at least one order. Find $P(A)$, $P(B)$, $P(A \cup B)$, and $P(A \cap B)$ by summing the probabilities of the sample points in these events.
\end{enumerate}

\section*{Solution}

\begin{enumerate}
	\item
		\begin{table}[h]
			\centering
			\begin{tabular}{ccc}
				$(V_1, V_1)$ & $(V_2, V_1)$ & $(V_3, V_1)$ \\
				$(V_1, V_2)$ & $(V_2, V_2)$ & $(V_3, V_2)$ \\
				$(V_1, V_3)$ & $(V_2, V_3)$ & $(V_3, V_3)$ \\
			\end{tabular}
		\end{table}
	\item $\frac{1}{9}$
	\item
	$$
		\begin{aligned}
			A: & \{ (V_1, V_1), (V_2, V_2), (V_3, V_3) \} \\
			B: & \{ (V_1, V_2), (V_2, V_1), (V_2, V_2), (V_2, V_3), (V_3, V_2) \} \\
			P(A) & = \frac{3}{9} = \frac{1}{3} \\
			P(B) & = \frac{5}{9} \\
			P(A \cup B) & = \frac{7}{9} \\
			P(A \cap B) & = \frac{1}{9}
		\end{aligned}
	$$
\end{enumerate}

\newpage

\section*{Question 4 (25 pts.)}

A manufacturer has nine motors in stock, two of which are defective. The manufacturer receives three separate orders for three engines per order. If the engines are randomly assigned to each order, what is the probability that all two defective engines are assigned to the first order?

\section*{Solution}

$$
	\begin{aligned}
		N & = {9 \choose 3 3 3} = \frac{9!}{3!3!3!} = \frac{9 \cdot 8 \cdot 7 \cdot 6 \cdot 5 \cdot 4}{3 \cdot 2 \cdot 3 \cdot 2} \\
		& = \frac{9 \cdot 8 \cdot 7 \cdot 5 \cdot 4}{6} = 1680 \\
		n_a & = {2 \choose 2}{7 \choose 1 3 3} = \frac{7!}{1!3!3!} = \frac{7 \cdot 6 \cdot 5 \cdot 4}{6} \\
		& = 7 \cdot 5 \cdot 4 = 140
		P(A) = \frac{n_a}{N} = \frac{140}{1680} = 0.0833
	\end{aligned}
$$

\end{document}
