% Template from https://www.overleaf.com/latex/templates/chapter-review-notes/npqqbrvfkwqh
\documentclass[11pt]{article}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}	
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{multirow,booktabs}
\usepackage[table]{xcolor}
\usepackage{fullpage}
\usepackage{lastpage}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{wrapfig}
\usepackage{setspace}
\usepackage{calc}
\usepackage{multicol}
\usepackage{cancel}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage[margin=3cm]{geometry}
\usepackage{amsmath}
\newlength{\tabcont}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}
\usepackage{empheq}
\usepackage{framed}
\usepackage[most]{tcolorbox}
\usepackage{xcolor}
\colorlet{shadecolor}{orange!15}
\parindent 0in
\parskip 12pt
\geometry{margin=1in, headsep=0.25in}
\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{reg}{Rule}
\newtheorem{exer}{Exercise}
\newtheorem{note}{Note}
\begin{document}
\title{Title}

\thispagestyle{empty}

\begin{center}
{\LARGE \bf Homework 1} \\
{\large Probability \& Statistics} \\
{\large Due June 4th}
\end{center}
\section*{Problem 1 (2 pts.)}

For more than a century, normal body temperature for humans has been accepted to be 98.6\degree \space Fahrenheit. Is it really? Researchers want to estimate the average temperature of healthy adults in the United States.

\begin{enumerate}
	\item What is the population for this experiment?
	\item List three possible samples for this experiment. \textit{Hint: We aren't always interested in completely random samples. Should we look at the same number of men and women? What about other aspects to consider?}
\end{enumerate}

\section*{Problem 2 (4 pts.)}

An archaeologist is interested in the percentage of aluminum oxide in pottery. The archaeologist selects 5 different pottery items and finds that they have the following percentages of aluminum oxide: 17.7, 18.3, 16.7, 14.8, 19.1.

\begin{enumerate}
	\item Calculate the average, $\bar{y}$, for the sample. (Show all work.)
	\item Calculate the variance, $s^2$, for the sample. (Show all work.)
	\item Calculate the standard deviation, $s$, for the sample.
	\item Assume the percentages of aluminum oxide are normally distributed (bell-shaped). What range of aluminum oxide percentages would we expect approximately every pottery item to fall within?
\end{enumerate}

\section*{Problem 3 (4 pts.)}

A box contains three marbles: one red, one green, and one blue. Consider an experiment that consists of taking one marble from the box then replacing it in the box and drawing a second marble from the box.

\begin{enumerate}
	\item What is the sample space?
	\item If each marble in the box is equally likely to be selected, what is the probability of each point in the sample space?
\end{enumerate}

\end{document}
